Kindly Bent to Free Us

### 2019-11-18 kindly/motivation.tex
Misc.

We now showcase an API for mutable linear arrays
(\cref{sig:array}).
The intention of this API is to safely handle manual allocation and
deallocation of arrays that may contain affine elements.
One would first use @create n v@ to create
an (unrestricted) array of size @n@ initialized with value
@v@. This value must be unrestricted as it is duplicated to
initialize all array elements. Using the @map@ function we
can transform the unrestricted elements into linear (affine)
ones. This array can be processed further using @map@ (or @set@ if
affine). The @get@ function is only applicable if the element type
is unrestricted as one element is duplicated. The @length@
function is always applicable. To @free@ an array the elements must be
affine.

@@

This encapsulation is implemented with a universally quantified \emph{kind index variable} $r$.
The signature prescribes the type @&!(aff_r1,'a_1)@ for the
exclusive borrow of the resource with an affine kind at region nesting $r+1$. The return
type of the callback is constrained to kind @'k_2 <= aff_r@
so that the callback certainly cannot return the borrowed argument.
In a specific use of @Pool.use@, the index $r$ gets unified
with the current nesting level of regions so that the region for the
callback effectively gets ``inserted'' into the lexical nesting at the callsite.

\cref{ex:pool} shows a simple example of using the @Pool@ module.

>>>>

The API for mutable linear arrays (shown in \cref{sig:array})
aims to safely handle manual allocation and
deallocation of arrays that may contain affine elements.
One would first use @create n v@ to create
an (unrestricted) array of size @n@ initialized with value
@v@. This value must be unrestricted as it is duplicated to
initialize all array elements. Using the @map@ function we
can transform the unrestricted elements into linear (affine)
ones. This array can be processed further using @map@ (or @set@ if
affine). The @get@ function is only applicable if the element type
is unrestricted as one element is duplicated. The @length@
function is always applicable. To @free@ an array the elements must be
affine.

@@

This encapsulation is implemented with a universally quantified \emph{kind index variable} $r$.
The signature prescribes the type @&!(aff_r1,'a_1)@ for the
exclusive borrow of the resource with an affine kind at region nesting $r+1$. The return
type of the callback is constrained to kind @'k_2 <= aff_r@
so that the callback certainly cannot return the borrowed argument.
In a specific use of @Pool.use@, the index $r$ gets unified
with the current nesting level of regions so that the region for the
callback effectively gets ``inserted'' into the lexical nesting at the callsite.
%
\cref{ex:pool} shows a simple example using the @Pool@ module.
